---
title: "Assignment6"
author: "Dana Jensen"
date: "October 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 2 - Part 1 - Assessing voice in schizophrenia

N.B. Question to be answered via email to Celine: can you characterize voice in schizophrenia as acoustically different? 

Report the methods you used to answer this question and the results from the analyses. Add a couple of lines trying to interpret the results (make sense of the difference). E.g. People with schizophrenia tend to have high-pitched voice, and present bigger swings in their prosody than controls. Add a couple of lines describing limitations of the data/analyses if any is relevant.

N.B. There are looots of files to be dealt with. Probably too many for your computer. This is a challenge for you. Some (complementary) possible strategies: You can select a subset of files only (and you have to justify your choice). You can learn how to use the apply() or map() functions. 

1. In the course of this assignment you have to first select one datafile and figure out how to:

- Extract "standard" descriptors of pitch: Mean, standard deviation, range
- Extract less "standard" descriptors of pitch you can think of (e.g. median, iqr, mean absoluted deviation, coefficient of variation)
- Extract "complex" descriptors: recurrence quantification analysis

2. Second you will have to turn the code into a function and loop through all the files (or even better use apply/sapply/lapply)
- Remember to extract the relevant information from the file names (Participant, Diagnosis, Trial, Study)

3. Make one model per acoustic feature and test whether you can observe significant difference due to Diagnosis. Tip: Which other fixed factors should you control for (that is, include in the model)? Which random ones?
- Bonus points: cross-validate the model and report the betas and standard errors from all rounds to get an idea of how robust the estimates are. 
3a. Is study a significant predictor in these models? What should you infer from this? Does study interact with diagnosis? What should you infer from this?

4. Bonus Question: Compare effect size of diagnosis across the different measures. Which measure seems most sensitive?
- Tip: to compare across measures you need to put all of them on the same scale, that is, you need to "standardize" them (z-score)

5. Bonus question. In the Clinical Info file you have additional information about the participants. Which additional parameters (e.g. age, gender) should we control for? Report the effects.

6. Write a paragraph reporting methods and results

## N.B. Remember to save the acoustic features of voice in a separate file, so to be able to load them next time

Recurrance rate - how much is covered in black? (%)
Determinisim - stability of repetitions, how likely black dot is not isolated,
but part of a diagonal (keeps repeating)
L - how long do shared directories go together?
Lmax - maximum trajectory
Entropy - when system repeats itself? How unpredictable?
Laminarity - Verticle patterns (getting stuck)
Trapping Time - how long you are 'trapped' in the state (verticle)
```{r}
#prelude
path<-("C:/Users/Dana/Desktop/METHODS III/AssignmentVI")
setwd(path)
library(pacman)
p_load(Pastecs, stats, lsr, nonlinearTseries, crqa, readr, stringr, lmerTest)
folder = file.path(path)
pitch_list<- list.files(path = folder, recursive = TRUE, pattern = "*f0.txt")

#-------------------------------------------------------------------------
##Extract "standard" descriptors of pitch: Mean, standard deviation, range
##Extract less "standard" descriptors of pitch you can think of (e.g. median, iqr, mean absoluted deviation, coefficient of variation)

summary.list = function(x){
  result<-c(
  Mean=mean(x$f0, na.rm=TRUE),
  Median=median(x$f0, na.rm=TRUE),
  Max.Min=range(x$f0, na.rm=TRUE),
  Range=max(x$f0, na.rm=TRUE) - min(x$f0, na.rm=TRUE),
  Variance=var(x$f0, na.rm=TRUE),
  Std.Dev=sd(x$f0, na.rm=TRUE),
  IQR=IQR(x$f0, na.rm = TRUE),
  MeanAbsDev=aad(x$f0, na.rm = TRUE),
  Coeff.Variation.Prcnt=sd(x$f0, na.rm=TRUE)/mean(x$f0, na.rm=TRUE)*100,
  Std.Error=sd(x$f0, na.rm=TRUE)/sqrt(length(x$f0[!is.na(x)])),
  Quantile=quantile(x$f0, na.rm=TRUE)
  )
  
return(result)
}
p = read.delim(pitch_list[1])
summary.list(p)
#-----------------------------------------------------------------------
##Extract "complex" descriptors: recurrence quantification analysis
rqa_analysis= function(x)(  
  crqa(x, x, embed = 2, delay = 1, normalize = 0, rescale = 0, radius = 0.5,
  mindiagline = 2, minvertline = 1)
)
rqa_analysis(p)

#-----------------------------------------------------------------------
##a function and loop through all the files (or even better use apply/sapply/lapply). Remember to extract the relevant information from the file names (Participant, Diagnosis, Trial, Study)

filename = NULL
temp = NULL
id =  NULL
study = NULL
diagnosis = NULL
trial = NULL
mean= NULL
median= NULL
max.min = NULL
range = NULL
variance= NULL
std.dev= NULL
IQR= NULL
coeff.variation.prcnt= NULL
std.error= NULL
quantile= NULL
radius= NULL
delay= NULL
embed= NULL

n = 1

for (file in pitch_list){
  #practical information
  filename = file
  i = read_delim(file, delim = "\t")
  temp[n] = paste(folder, i, sep = "")
  id[n] =  str_extract(str_extract(file, "S\\d+"), "\\d+")
  study[n] = str_extract(str_extract(file,"\\S\\w{4}\\d{1}"), "\\d")
  diagnosis[n] = str_extract(str_extract(file, "D\\d"), "\\d")
  trial[n] = str_extract(str_extract(file, "T\\d+"), "\\d+")
  #some numbers
  mean[n]= mean(i$f0)
  median[n]= median(i$f0)
  max.min[n]= range(i$f0)
  range[n]= max(i$f0) - min(i$f0)
  variance[n]= var(i$f0)
  std.dev[n]= sd(i$f0)
  IQR[n]= IQR(i$f0)
  coeff.variation.prcnt[n]= sd(i$f0)/mean(i$f0)*100
  std.error[n]= sd(i$f0)/sqrt(length(i))
  quantile[n]= quantile(i$f0)
  # and now for something completely different...
  V = try(optimizeParam(i, i, par, min.rec = 3.5, max.rec = 4.5))
  if (length(V)>1){
    radius[n]= V$radius
    delay[n]= V$delay
    embed[n]= V$emddim}
  else{ 
    radius[n] = NA
    delay[n] = NA
    embed[n] = NA}
  
  n = n+1
}

dframe<- data.frame(filename, id, study, diagnosis, trial, mean, median, variance, std.dev, IQR, coeff.variation.prcnt, std.error, quantile, radius, delay, embed)

#----------------------------------------------------------------------------
##3. Make one model per acoustic feature and test whether you can observe significant difference due to Diagnosis. Tip: Which other fixed factors should you control for (that is, include in the model)? Which random ones?

model1 = glmer(diagnosis ~ range + trial + variance (1+trial|id), data = dframe, family = 'binomial')

##3a. Is study a significant predictor in these models? What should you infer from this? Does study interact with diagnosis? What should you infer from this?


##Bonus points: cross-validate the model and report the betas and standard errors from all rounds to get an idea of how robust the estimates are. 





  
```
